Challenges in Developing Great Quasi-Monte Carlo Software

### 2023-03-14 MCQMC2022ChallengesQMCSoftwareArticle.tex
sc: Added examples in Section 5.

\section{Efficient} \label{CDHJS_sec:efficient}
Another obvious feature of great QMC software is numerical efficiency.  This requires developers to identify bottlenecks in performance.  Intensive computations may need to be rewritten in lower-level languages, like C.  Code may need to be refactored to avoid excessive calls to memory.  As new hardware architectures arise, QMC software should adapt to take advantage of them.

Efficiency gains in QMC software can also result from clever algorithm choices.  The Bayesian stopping rules for lattice and Sobol sequences in \cite{RatHic19a,JagHic22a} choose covariance kernels that match the corresponding LD sequence.  This reduces the computations from what would be $\calO(n^3)$ for arbitrary covariance kernels to only $\calO(n \log n)$ for these well-chosen kernels. Consequently, computing the stopping criterion is roughly the same order of magnitude as computing the solution.

@@

Great software should be stored in a repository, where the latest version can be downloaded.  There should be documentation that guides the user through installation and explains the library's features.  Demos are crucial for showing how the software works and for providing a template for new users to write their own code.  Tutorials help newcomers to QMC understand its advantages. Blogs educate a wider audience and enlarge our QMC community.  A suite of unit tests should be run regularly to ensure that new features do not introduce bugs. There should be a place for users to report bugs and make feature requests.

>>>>

\section{Efficient} \label{CDHJS_sec:efficient}
Another obvious feature of great QMC software is computational efficiency.  This requires developers to identify bottlenecks in performance.  Intensive computations may need to be rewritten in lower-level languages, like C.  Code may need to be refactored to avoid excessive calls to memory.  As new hardware architectures arise, QMC software should adapt to take advantage of them.

Efficiency gains in QMC software can also result from clever algorithm choices. \SCComment{Adaptive QMC algorithms as in \cite{JimHic16a, HicJim16a, HicEtal17a} can be used to dynamically increase the number of sampling points based on estimated error bounds. They can lead to significant efficiency gains by reducing the number of unnecessary function evaluations.} The Bayesian stopping rules for lattice and Sobol sequences in \cite{RatHic19a,JagHic22a} choose covariance kernels that match the corresponding LD sequence.  This reduces the computations from what would be $\calO(n^3)$ for arbitrary covariance kernels to only $\calO(n \log n)$ for these well-chosen kernels. Consequently, computing the stopping criterion is roughly the same order of magnitude as computing the solution.

@@

Great software should be stored in a repository, where the latest version can be downloaded.  There should be documentation that guides the user through installation and explains the library's features.  Demos are crucial for showing how the software works and for providing a template for new users to write their own code.  Tutorials help newcomers to QMC understand its advantages. Blogs educate a wider audience and enlarge our QMC community.  A suite of unit tests should be run regularly to ensure that new features do not introduce bugs.\SCComment{Move the last sentence to section on Correct} There should be a place for users to report bugs and make feature requests.
